\documentclass[12pt]{amsart}

%%% Packages
\usepackage{amsmath,amssymb,amsthm}
\usepackage{booktabs}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{array}
\usepackage{float}
\usepackage[colorlinks=true,citecolor=blue,urlcolor=blue,linkcolor=blue]{hyperref}

%%% Fix overflow: allow generous line breaking
\emergencystretch=1.5em
\sloppy

%%% Figures path
\graphicspath{{../../experiments/figures/}}

%%% Theorem environments
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{observation}[theorem]{Observation}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}

%%% Math operators and macros
\DeclareMathOperator{\lcm}{lcm}
\DeclareMathOperator{\CS}{CS}
\DeclareMathOperator{\FMC}{FMC}
\newcommand{\NH}{N_H}
\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\ceil}[1]{\left\lceil #1 \right\rceil}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\norm}[1]{\left\| #1 \right\|}
\newcommand{\eps}{\varepsilon}
\newcommand{\de}{\delta}

\subjclass[2020]{11B83, 05C70, 11N25, 05D15}

\keywords{Erd\H{o}s Problem 710, divisible injection, Hall's marriage theorem,
  Cauchy--Schwarz, bipartite matching, smooth numbers}

\title[Approaches to Erd\H{o}s--Pomerance]{Computational and analytic approaches to the Erd\H{o}s--Pomerance divisible injection problem}

\author{Steven Tolbert}

\date{February 2026}

\begin{document}

\begin{abstract}
We report on an extensive computational and analytic investigation of
Erd\H{o}s Problem~\#710: determine $f(n)$, the minimum length~$L$ such that
there exists an injection $\varphi\colon \{1,\ldots,n\}\to (n,n+L]\cap\mathbb{Z}$
with $k\mid\varphi(k)$ for all~$k$. The conjectured answer is
$f(n) = (2/\sqrt{e}+o(1))\,n\sqrt{\ln n/\ln\ln n}$, where the lower bound
is due to Erd\H{o}s and Pomerance. We verify computationally that the
matching upper bound holds for all $n\le 10^6$ via exhaustive
Hopcroft--Karp matching with zero failures. For the analytic regime
$n\to\infty$, we document 43~distinct approaches---including Cauchy--Schwarz
variants, fractional matching, the Lov\'asz Local Lemma, spectral methods,
sieve bounds, semi-random nibble, and graph-theoretic techniques---each of
which fails to close the gap between per-interval Hall verification and
global Hall's condition. We identify the precise structural obstruction:
the worst-case subset~$T^*$ spans approximately~48--53\% of vertices,
drawn from \emph{all} dyadic intervals at roughly~60\% density per interval,
with expansion ratio barely exceeding~$1$.
We catalog every approach, its failure mechanism, and the computational
evidence, with the aim of guiding future work on this long-standing open
problem.
\end{abstract}

\maketitle
\tableofcontents

%% ============================================================
\input{section_01_introduction}
\input{section_02_construction}
\input{section_03_proved}
\input{section_04_gap}
\input{section_05_cauchy_schwarz}
\input{section_06_matching}
\input{section_07_probabilistic}
\input{section_08_sieve}
\input{section_09_graph_theoretic}
\input{section_10_phenomena}
\input{section_11_initial_attempt}
\input{section_12_conclusion}

%% ============================================================
%% Bibliography
%% ============================================================
\begin{thebibliography}{99}

\bibitem{Erdos1938}
P.~Erd\H{o}s, On sequences of integers no one of which divides the product
of two others and on some related problems,
\emph{Mitt.\ Forsch.-Inst.\ Math.\ Mech.\ Univ.\ Tomsk} \textbf{2} (1938), 74--82.

\bibitem{ErdosPomerance1980}
P.~Erd\H{o}s and C.~Pomerance,
Matching the natural numbers up to~$n$ with distinct multiples in another interval,
\emph{Nederl.\ Akad.\ Wetensch.\ Proc.\ Ser.~A} \textbf{83} (1980), 147--161.

\bibitem{ErdosSarkozy1966}
P.~Erd\H{o}s, A.~S\'ark\"ozy, and E.~Szemer\'edi,
On divisibility properties of sequences of integers,
\emph{Studia Sci.\ Math.\ Hungar.} \textbf{1} (1966), 431--435.

\bibitem{Hall1935}
P.~Hall, On representatives of subsets,
\emph{J.\ London Math.\ Soc.} \textbf{10} (1935), 26--30.

\bibitem{HopcroftKarp1973}
J.\,E.~Hopcroft and R.\,M.~Karp,
An $n^{5/2}$ algorithm for maximum matchings in bipartite graphs,
\emph{SIAM J.\ Comput.} \textbf{2}(4) (1973), 225--231.

\bibitem{Ford2008}
K.~Ford, The distribution of integers with a divisor in a given interval,
\emph{Ann.\ of Math.} (2) \textbf{168} (2008), 367--433.

\bibitem{KoukoulopoulosMaynard2020}
D.~Koukoulopoulos and J.~Maynard,
On the Duffin--Schaeffer conjecture,
\emph{Ann.\ of Math.} (2) \textbf{192} (2020), 251--307.

\bibitem{HildebrandTenenbaum1993}
A.~Hildebrand and G.~Tenenbaum,
Integers without large prime factors,
\emph{J.\ Th\'eor.\ Nombres Bordeaux} \textbf{5} (1993), 411--484.

\bibitem{Rodl1985}
V.~R\"odl, On a packing and covering problem,
\emph{European J.\ Combin.} \textbf{6} (1985), 69--78.

\bibitem{MolloyReed2002}
M.~Molloy and B.~Reed,
\emph{Graph Colouring and the Probabilistic Method},
Springer, Algorithms and Combinatorics~23, 2002.

\bibitem{Haxell1995}
P.\,E.~Haxell, A condition for matchability in hypergraphs,
\emph{Graphs Combin.} \textbf{11} (1995), 245--248.

\bibitem{ErdosSpencer1991}
P.~Erd\H{o}s and J.~Spencer,
Lopsided Lov\'asz Local Lemma and Latin transversals,
\emph{Discrete Appl.\ Math.} \textbf{30} (1991), 151--154.

\bibitem{Janson1998}
S.~Janson, New versions of Suen's correlation inequality,
\emph{Random Structures Algorithms} \textbf{13} (1998), 467--483.

\bibitem{Erdos1990}
P.~Erd\H{o}s, Some of my favourite unsolved problems,
in \emph{A Tribute to Paul Erd\H{o}s} (A.~Baker, B.~Bollob\'as,
A.~Hajnal, eds.), Cambridge University Press, 1990, pp.~467--478.

\bibitem{Guy2004}
R.\,K.~Guy, \emph{Unsolved Problems in Number Theory}, 3rd~ed.,
Springer, 2004.

\end{thebibliography}

\end{document}
